Text Detection and Chinese Character Recognition in Natural Scene Images via Pre-trained Vision and Language Models

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1.fix some typo mistakes for x.

  Detecting and reading text from natural scene images is an essential computer vision tasks.
  Giving the fact that Chinese characters have more tokens than English characters, OCR in Chinese is much harder than English.
  I encode high dimension features extracting from images by ResNet followed by the pre-trained language models of
  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $77.24\%$ on the Baidu2019 street scene test set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|r|}
\hline
Model & Dim & Dataset& Epochs & Accuracy \\
\hline\hline
ResNet      & 18 &  ICDAR2015     & 50 &	23.67\% \\
ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
ResBertNet  & 18+3 & Baidu2019    & 64	&	77.24\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset and the ICDAR2015 dataset.
The ResBertNet uses 18 layers of Residual Network and 3 layers of Transformers.}
\end{table}

@@

This paper proposes a novel idea by using pre-trained language models for Chinese scene text detection and recognition.
The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
the model achieved accuracy of $77.24\%$ on the Baidu 2019 street view text recognition set.

>>>>

  Detecting and reading text from natural scene images is an essential computer vision tasks.
  Giving the fact that Chinese characters have more tokens than English characters, OCR in Chinese is much harder than English.
  I encode high dimension features extracting from images by ResNet followed by the pre-trained language models of
  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $79.82\%$ on the Baidu2019 street scene test set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|r|}
\hline
Model & Dim & Dataset& Epochs & Accuracy \\
\hline\hline
ResNet      & 18 &  ICDAR2015     & 50 &	23.67\% \\
ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
ResBertNet  & 18+3 & Baidu2019    & 72	&	79.82\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset and the ICDAR2015 dataset.
The ResBertNet uses 18 layers of Residual Network and 3 layers of Transformers.}
\end{table}

@@

This paper proposes a novel idea by using pre-trained language models for Chinese scene text detection and recognition.
The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
the model achieved accuracy of $79.82\%$ on the Baidu 2019 street view text recognition set.
